\section{Leadership}
Leadership is a process by which an executive can direct, guide and influence the behavior and work of others
towards accomplishment of specific goals in a given situation. Leadership is the ability of a manager to induce
the sub-ordinates to work with confidence and zeal. It is the potential to influence behavior of others. It is also
defined as the capacity to influence a group towards the realization of a goal. Leaders are required to develop
future visions and to motivate the organizational members to want achieve the visions.
According to Keith Davis, “Leadership is the ability to persuade others to seek defined objectives
enthusiastically. It is the human factor which binds a group together and motivates it towards goals.”
Characteristics of Leadership are as follows:
\begin{enumerate}
\item It is an interpersonal process in which a manager is influencing and guiding workers towards attaining
goals.
\item It denotes a few qualities to be present in a person which includes intelligence, maturity and
personality.
\item It is a group process. It involves two or more people interacting with each other.
\item A leader is involved in shaping and molding the behavior of the group towards accomplishment of
organizational goals.
\item Leadership is situation bound. There is no best style of leadership. It all depends upon tackling with
the situations.
\end{enumerate}
Leadership is an important function of management which helps to maximize efficiency and to achieve
organizational goals. The following points justify the importance of leadership in a concern.

\begin{itemize}
\item Initiates action
\item Motivation
\item Providing guidance
\item Creating confidence
\item Building morale
\item Builds work environment
\item Co-ordination
\end{itemize}
Verscend Information Technologies promotes effective leadership. The organization believes in a leader who:
is committed on personal and professional front, and is responsible. He must be a role model for other
staffs.
\begin{itemize}
\item
Has the capability to boost up the morale of his/her employees. He/she should motivate them so that
they are committed to the organization. He/she should be well acquainted with them, have concern for
them and encourage them to take initiatives. This will result in more efficient and effective employees
and ensure organizational success.
\item
Must work as a team. He/she should always support his/her team and respect team players. He/she
should not hurt any employee. A true leader should not be too bossy and should not consider him/her
as the supreme authority. He/she should realize that he/she is part of the organization as a whole.
\end{itemize}
\cleardoublepage
