\section{Motivation}
Motivation is derived from the word ‘motive’ which means needs, desires, wants or drives within an
individual. It is the process of stimulating people to actions to accomplish the goals. In the work goal context,
the psychological factors stimulating the people’s behavior can be desire for money, success, recognition, job
satisfaction, team work, etc. One of the most important functions of management is to create willingness
amongst the employees to perform in the best of their abilities. Therefore the role of a leader is to arouse
interest in performance of employees in their jobs. The process of motivation consists of three stages:
\begin{enumerate}
\item A felt need or drive
\item A stimulus in which needs have to be aroused
\item When needs are satisfied, the satisfaction or accomplishment of goals.
\end{enumerate}
Therefore, we can say that motivation is a psychological phenomenon which means that needs and wants of
individuals have to be tackled by framing an incentive plan.
Motivation is very important for an organization because of the following benefits it provides:
\begin{itemize}
\item Puts human resources into action
\item Improves level of efficiency of employees
\item Leads to achievement of organizational goals
\item Builds friendly relationship
\item Leads to stability of workforce
\end{itemize}
Employees are the building blocks of an organization. Organizational success depends on the collective efforts
of the employees. The employees will collectively contribute to organizational growth when they are
motivated. Below mentioned are some of ways Verscend Technologies has undertaken to keep its
workplace motivated.
\begin{itemize}
\item  Giving the employees learning opportunities:\\ Employees should consistently learn new skills in the
job. Continuing learning is the best way to remain employable. So,Verscend Technologies
provides several opportunities to its employees to develop their skills and competencies and to make
best use of their skills. It also links the staff goals with the organizational goals.
\item  Develop and encourage creativity: \\ The company encourages its staff to develop creativity skills so
as to solve organizational problems. It gives employees time and resources for developing creativity.
It also lets them hold constant brainstorming sessions and invites ideas and suggestions from the staff.
\item  Respecting team: \\ The company respect not only the employees’ rights to share and express their
views and to be themselves, but also their valuable time. It makes the staff feel that they are respected
not just as an employee/worker but also as an individual.
\item  Provides the employees with certain benefits: \\ The company gives its staff ample amount of financial
and other benefits. It offers them bonuses, pay them for overtime,
and give them health and family insurance benefits. It ensures that they get breaks from work and lets
them enjoy vacations and holidays.
\item  Acknowledge staff on their achievements: \\ A pat on the back, some words of praise, and a note of
credit to the employee/staff member at personal level with some form of broad publicity can motivate
the staff a lot. So,Verscend Technologies makes sure to acknowledge its staff's great
achievements. It not only acknowledges the employee with highest contribution, but also acknowledge
the employee who meets and over exceeds the targets.
\item  Ensuring that employees are interested in their jobs: \\ This means assigning tasks that are
meaningful and somewhat challenging to person. So,Verscend Technologies makes sure
that its employees are satisfied with the type of job they are doing.
\end{itemize}
\cleardoublepage

