\section{Organization}
\subsection{Introduction}
Verscend Technologies, situated at Hattisar Sadak, Kathmandu is a software research and development center for Verscend Analytics, the parent company based in the USA. Verscend Analytics is a leading data analytics provider offering risk assessment services and decision analytics in fields like property/casualty insurance, reinsurance, mortgage, financial services, healthcare, government and corporate risk management. \\
As a US offshore company, Verscend Technologies builds enterprise systems and provide state-of-the-art solutions for the Verscend Family of Companies. Verscend Technologies is involved in the design, development, testing and maintenance of impressive lineup of trend-setting products of Verscend member companies like Verscend Health, ISO, 3E and other that help customers protect people, property, and financial assets in the US and around the world.
\subsection{History}
In 2008, Verscend Analytics was established to serve as the parent holding company of ISO(Insurance Service Office). ISO was created in 1971 through the consolidation of various, regional, and national rating bureaus for various lines of property/casualty insurance. ISO helps insurers with product developement, underwriting and rating.
\subsection{Objective}
The main goal of the company is to cater research and development services to Verscend Analytics. The
objectives of the company are:
\begin{itemize}
\item To collect and analyze billions of records and draws on vast industry expertise and unique proprietary
datasets
\item To provide predictive analytics and decision support solutions in fraud prevention, actuarial science,
insurance coverage, catastrophe and many other fields
\item To design and develop top notch applications.
\item To establish and maintain robust database of information on losses, claims, costs, etc. that supplements
world-class decision support system.\end{itemize}
\subsection{Input}
The company offers its products and services – to a number of industries to help risk bearing businesses
understand and manage their risks – which include property/casualty insurance, financial services, healthcare,
government, and human resources.
\subsection{Process}
The company works on following to provide the effective products and services to it's clients:
\begin{itemize}
\item Company Market
\item P/C Insurance
\item Financial Services
\item Commercial Real Estate
\item Community Hazard Mitigation
\item Climate Risk
\end{itemize}
\subsection{Output}
The services offered by a compnay can be categorized into two major reporting segments :
\begin{itemize}
\item Risk assessment:\\The risk assessment business serves customers in property/casualty industry by helping them define,
measure and manage risk.  
\item Decision analytics:\\ The decision analytics business serves customers in a variety of industries with tool
that help them make informed decision about managing their assets and the associated risk in predicting future
losses, selecting and pricing risk, detecting and preventing fraud and quantifying losses that have already
happened.

\end{itemize}
\cleardoublepage
