\section{Personnel Management}
\subsection{Personnel Policies}
Personnel policies define the treatment, rights, obligations, and relations of people in an organization. They
are the blueprints by which the organization runs: the rules and procedures that protect workers and the
organization from being abused, put them in control of their jobs, and keep them from making errors that will
hurt the organization or one another. They touch on relationships \big( staff/staff, staff/administration, etc.\big),
expectations \big( hours worked, schedules, what defines the work of a position\big), and ways of doing things \big(who
gets to use what equipment when, how to arrange a sick day \big) that affect employees' lives and the running of
the organization.
There are essentially three types of personnel policies:
\begin{itemize}
\item
General Policies: These policies include the basic structure, philosophy, and rules of the organization.
They deal with issues ranging from equal opportunity in hiring and advancement to conflicts of
interest, sexual harassment, alcohol in the workplace and Internet usage.
\item
Hiring and Employment Status Policies: These policies include the worker's employment
relationship with the organization - hiring, firing and everything in between. Here is where pay scale,
title, promotions and performance reviews are laid out. These policies also cover benefits, employees'
rights and reasons for termination.
\item
Everyday Procedural Policies: These policies deal with issues that affect the everyday life of the
worker or volunteer, and the day-to-day operation of the organization. They generally include the
hours employees are required to be at work, how workers should dress, when they get paid, and issues
of security as well as guidelines for how things are done in the organization.\\
\\Policies followed by Verscend Technologies are:
\item
Training and Orientation: At Verscend Technologies, employees, once hired, typically go
through an orientation and training process to learn about their new employer and how their job
function fits into the overall goals of the business. During this time, employees may attend training
sessions, get assigned a mentor or participate in a virtual training session provided by the company
such that new employees understand and are well prepared for their new positions.
\item
Work Schedule, Breaks and Leave: Verscend Technologies provides guidelines for when
an employee should report to the office for work and when he/she should leave. These policies also
include the procedures for calling in sick, information on jury duty and how time off for bereavement
is handled.
\item
Salaries and Pay Schedule: Employees at Verscend Technologies have diverse salaries,
including salary ranges or a salary scale. These policies give employees an idea of how much money
they can potentially make, if promoted. Employees are paid in monthly basis and have with them
a
written documentation that outlines their pay schedules.
\item
Performance Reviews and Promotions:Verscend Technologies has maintained
performance sheet to monitor the performance of its employees. The performance can be reported from
supervisor level and by employee themselves. Organizational commitment of the employee is also a
major factor that is included in the policy which determines the remuneration of the employee. This
policy also states the fact that when the employee can expect a raise in salary and in what basis.
\item Terminating Employment:Verscend Technologies also has policies that state how
employees or employers can terminate employment at the company. The policies also outline how
much advance notice must be given and in what format, as well as information on severance packages,
returning company keys and equipment and ending access to company records.
\end{itemize}
\subsection{Manpower Planning}
Manpower can be defined as the sum total of the skills, talents, knowledge, qualifications, creativity, ability
and the values of the workforce of an organization. Manpower planning, also called as human resource
planning stands for putting right number of individuals, right kind of individuals, at right place, right time,
doing the right job they are suitable for.
\\In Verscend Technologies, the following general procedures are followed for manpower planning:
\begin{enumerate}
\item
 Analyzing of current manpower inventory.
\item
 Making future manpower forecasts based on workload analysis, budget and planning analysis, needs
of experts etc.
\item
 Devieloping Employment programs like recruitment, hiring, selections and placements.
\item
 Desiigning training programs.
\end{enumerate}
\subsection{Recruitment and Selection of Manpower}
Recruitment is the process of acquiring required number and types of individuals necessary to ensure
continued progress and operation of the organization.Verscend Technologies has recruitment
policies for both students and professionals. Students are recruited as interns while professionals or pass out
students are hired for jobs. And all these actions are carried out by Human Resource Department. The
following are the steps in the company for recruitment and selection of manpower:
\begin{enumerate}
\item  Based on present needs and future plans, vacancy is advertised on different media like newspapers,
internet, job portals, etc.
\item  The applications are collected.
\item  Various levels of interviews and tests are conducted for the applicants. Some of the applicants are
selected after the preliminary interview. After the preliminary interview, the selected applicants are
tested for their technical skills and knowledge. The selected applicants from this test are almost sure
to be hired. However, a final interview is done to assess the attitude and psychological aspects of
the applicant.
\item  The applicants are then selected and appointed for job. They are introduced to the organization, the
tasks they need to fulfill, policies, rules and so on.
\item  Finally, the hired employee is assigned jobs.
\end{enumerate}
Verscend Technologies usually hire employees through \textbf{Internship, Trainee or Direct hire}.
\begin{itemize}
\item Internship: Verscend Technologies has a provision of paid internship for final year students
pursuing a Bachelor's degree. Every intern is assigned an experienced mentor who will be responsible
for mentoring of interns throughout the course of internship. High performing interns are offered
permanent employment.

\item Trainee: Throughout the year,Verscend Technologies conduct one to three months long
paid trainee programs in multiple batches. This program is ideal for fresh graduates who have “Can
do” attitude but lack experience. Trainees are provided hands-on training on areas that match both the
trainee’s as well as the company’s interest. High performing trainees are offered permanent
employment.

\item Direct Hire: For Direct hire, the company announces vacancy for required position and ask interested
candidates to apply. This program mainly focuses on hiring the expertise in the respected fields.
\end{itemize}
\subsection{Training and Skill Development of Manpower}
Training is an organized activity for increasing the knowledge and skills of people with an objective of
fulfilling a definite purpose. Training is a way for the development of manpower in an organization, which
leads people to do their jobs in a better way. Training has specific goals of improving one's capability,
capacity, productivity and performance.
Skill development is a training and development that the employer provides to his/her employees in the
workplace. It is often construed that only training that is provided by an outside training provider falls within
the definition of skill development. The definition also includes on-the-job training provided by the employer.
In VerscendTechnologies, the initial recruited employees or the interns are given special intensive
trainings to enhance their skills and knowledge to meet the organization’s goals.
Some of the techniques are specified below:
\begin{enumerate}
\item Training is given to new recruitments for specific period under the direct supervision.
\item Senior employees are also given intensive international trainings.
\item Challenging works are provided to the employees to make them more interested in their work.
\item Special opportunities are provided to cope with rapid changes in project environment.
\item New skills are developed by providing trainings on new technologies.
\end{enumerate}
\subsection{Job Evaluation}
Job evaluation is a systematic way of determining the value of a job in relation to other jobs in the organization.
It evaluates the skill, qualification, experience and efforts required to perform the job and forms the basis for
job hierarchy and the pay differentials.
The main objectives of job evaluation are:
\begin{enumerate}
\item  To formulate an appropriate and uniform wage structure.
\item  To clarify the responsibilities and authority associated with the job title.
\item  To provide a basis for recruitment, selection, promotion and transfer of employees.
\item  To identify the need for training employee so as to prepare them for future job.
\item  To eliminate the causes of dissatisfaction and conflicts among employees.
\end{enumerate}
For projects with high value, time allocation is comparatively larger and more workers are employed at the
company. Jobs which can boost the status of the company are given comparatively more attention.\\
The job evaluation model of VerscendTechnologies includes:
\begin{itemize}
	\item the level of bids won by company
	\item status of clients 
	\item economic worth of projects and all workers working within the company.\\
As per the worth of a project,workers are assigned on a categorized basis; Experienced employee may go for high value project, the trainees
and new workers may be assigned small project.
\end{itemize}
\subsection{Merit Rating}
Every four months, the performance of individuals is evaluated and rewarded. 20\% of the employees are given
best awards, 70\% of the deserving employees are given good increments.
\subsection{Wages and Incentives}
A wage is a monetary remuneration computed on hourly, daily, weekly basis or per standard output paid for
the service of labor. If paid in weekly or monthly basis, wage is called Salary. Wages and Salary include the
basic wage, allowances like family allowances, financial support, lunch allowances, holiday pay, overtime
pay, bonuses and other benefits.
An incentive is something that motivates an individual to perform certain action. The motive of incentive
programs is to increase the productivity of the employees and to help them enjoy work. Incentives not
necessarily mean just financial incentives, therefore, employees can be motivated through other non-monetary
incentives as well. Raise in pay, bonuses, rewards help employees be more motivated to their work.
\\ Verscend Information Technologies commits to provide sound and competitive salary to its employees. The salary is
particularly based on skills and capabilities of the employees rather than the position of the job. Even though
they have pre-defined specification of the payments for different jobs, deserving employees are provided with
higher payment.
 In addition to that, employees are
provided with free transportation and free medical facilities.
\cleardoublepage

