
\newpage
\phantomsection
\addcontentsline{toc}{section}{REFERENCES}
\begin{thebibliography}{9}
	\bibitem{dataset}
		D. Stillwell and M. Kosinski. (2017, January). myPersonality DataSet. Retrieved from \url{ http://mypersonality.org/wiki/doku.php}

 \bibitem{fivefactormodel}
	 Goldberg LR, et al. (2006). Five Factor Model of Personality:  \textit{The international personality item pool and the future of pulic-domain personality measures J Res Pers}, 40(1):8486.

 \bibitem{tupes}
 E. Tupes and R. Christal. (1992). Recurrent personality factors based on trait ratings. \textit{Journal of Personality}, 60(2): 225251.

 \bibitem{mccrae}
 R. McCrae and O. John. (1992). An introduction to the five-factor model and its applications. \textit{Journal of Personality}, 60(2): 175215.

 \bibitem{laplante}
 L. Audery. (2014). Improving music recommender systems: What can we learn from research on music tastes? \textit{ISMIR}.

 \bibitem{bruce}
 B. Ferwerda and S. Markus. (2014). Enhancing Music Recommender Systems with Personality Information and Emotional States: A Propoasal. \textit{UMAP Workshops}.

 \bibitem{melissa}
	 O. Melissa, A. Micareli and G. Sansonetti. (2016). A Comparative Analysis of Personaility Based Music Recommender Systems. \textit{EMPIRE RecSys}

 \bibitem{gonzalez}
 G. Gonzalez and M. Miquel. (2017). Embedding Emotional Context in Recommendation System. \textit{20th International Florida Artifical Intelligence Research Society Conference-FLAIRS}.

 \bibitem{resnick}
 P. Resnick and H. R. Vairan. (1997). Recommender Systems. \textit{Communications of the ACM}, 40(3):56-58.

 \bibitem{nunes}
Nunes, M.A.S.N. (2008). \textit{Recommender system based on personality traits}
\bibitem{kd}
	G. Parsa. (2017, July). Document Classification. Retrieved from \url{http://www.kdnuggets.com/2015/01/text-analysis-101-document-classification.html}
\bibitem{stopwords}
	Dropping common stop words. (2017, March). Retrieved from \url{http://nlp.stanford.edu/IR- book/html/htmledition/dropping-common-terms-stop-words-t1.html}
\bibitem{porter}
	M. F. Porter. (2001). Stemming Algorithm \textit{Snowball: A Language for Stemming Algorithms}
\bibitem{pos}
 Part of Speech Tagging. (2017, March). Retrieved from \url{http://en.wikipedia.org/wiki/Part-of-speech tagging}
 \bibitem{vector}
Textual data and vector space model. (2017, July). Retrieved from \url{http://www.calpoly.edu/~dsun09/lessons/textprocessing}

\bibitem{naive}
	Naive Bayes text classification. (2017, July). Retrieved from \url{https://nlp.stanford.edu/IR-book/html/htmledition/naive-bayes-text-classification-1.html}

\bibitem{additive}
	Additive Smoothing. (2017, July). Retrieved from \url{https://en.wikipedia.org/wiki/Additive_smoothing}

\bibitem{cross}
Cross Validation. (2017, July). Retrieved from \url{https://www.cs.cmu.edu/~schneide/tut5/node42.html}
\bibitem{analysis}
Data Analysis. (2017, February). Retrieved from \url{https://www.ngdata.com/what-is-data-analysis}

\bibitem{rdef}
 Recommender System. (2017, July). Retrieved from \url{http://recommender-system.blogspot.com/2012_10_01_archive.html}
 \bibitem{demographic}
	 L. Safoury and A. Salah. (2013). Exploiting user demographiattributes for solving cold-start problem in recommender system.\textit{Lecture Notes on Software Engineering}, 1(3), 303
\bibitem{recommend}
	A. Tejal. (2015). A Survey on Recommendation System. \textit{International Journal of Innovative Research in Advanced Engineering(IJIRA)}.
\bibitem{rmain}
	F. O. Isinkaye, Y. O. Folajimi and B. A. Ojokoh. (2015). Recommendation Systems: Principles, methods and evaluation \textit{Egyptian Informatics Journal}.
\bibitem{latent}
	Non-negative matrix factorization. (2017, July). Retrieved from \url{https://www.slideshare.net/BenjaminBengfort/non-negative-matrix-factorization}
\bibitem{manning}
C. Manning. (2017, June). Stanford NLP - Standford NLP Group. Retrieved from \url{https://nlp.standford.edu/manning}
\bibitem{coursera}
	Recommendation System, Coursera. (2017, July). Retrieved from \url{https://coursera.org/learn/machine-learning}
\bibitem{traits}
Studying the big five personality traits-UK Essays. (2017. January). Retrieved from \url{https://ukessays.com/essays/psychology/studying-the-big-five-personality-traits.php}

\bibitem{eval}
D. Alexander. (2009). Collaborative Fileringand Recommender Systems
\bibitem{tfidf}
TF-IDF. (2017, July). Retrieved from \url{http://www.tfidf.com/} 2015
\bibitem{api}
Facebook Graph API. (2017, July). Retrieved from \url{https://developers.facebook.com/docs/graph-api}
  \bibitem{ng}
  Andrew Ng. (2017, March). Machine Learning [Video lectures]. Retrieved from \url{https://www.coursera.org/learn/machine-learning}.

  \bibitem{wikilog}
  Logistic Regression. (n.d.). (2017, July). Retrieved from
  \url{https://en.wikipedia.org/wiki/Logistic_regression}.

  \bibitem{jason}
  Jason Brownlee. (2017, August). Logistic Regression for Machine Learning [Online tutorial].
  Retrieved from
  \url{http://machinelearningmastery.com/logistic-regression-for-machine-learning}.

\end{thebibliography}
