\newpage
\section{TOOLS AND TECHONOLOGIES}
\subsection{Python}
Python is a widely used high-level programming language for general-purpose programming. Python features a dynamic type system and automatic memory management and supports multiple programming paradigms, including object-oriented, imperative, functional programming, and procedural styles. It has a large and comprehensive standard library.

\subsection{Django}
Django is a free and open-source web framework, written in Python, which follows the model-view-template (MVT) architectural pattern. Django's primary goal is to ease the creation of complex, database-driven websites. Django emphasizes reusability and "pluggability" of components, rapid development, and the principle of don't repeat yourself. Python is used throughout, even for settings files and data models. Django also provides an optional administrative create, read, update and delete interface that is generated dynamically through introspection and configured via admin models.

\subsection{NumPy}
 NumPy is a library for the Python programming language, adding support for large, multi-dimensional arrays and matrices, along with a large collection of high-level mathematical functions to operate on these arrays.

\subsection{Pandas}
Pandas is a software library written for the Python programming language for data manipulation and analysis. In particular, it offers data structures and operations for manipulating numerical tables and time series. It offers wide range of features including DataFrame object for data manipulation with integrated indexing, tools for reading and writing data between in-memory data structures and different file formats, data alignment and integrated handling of missing data and more.

\subsection{Facebook Platform}
Facebook Platform is an umbrella term used to describe the set of services, tools, and products provided by the social networking service Facebook for third-party developers to create their own applications and services that access data in Facebook. The Graph API is the core of Facebook Platform, enabling developers to read from and write data into Facebook.

\subsection{HTML/CSS}
Hypertext Markup Language (HTML) is the standard markup language for creating web pages and web applications. Web browsers receive HTML documents from a web server or from local storage and render them into multimedia web pages. HTML describes the structure of a web page semantically and originally included cues for the appearance of the document.
Cascading Style Sheets (CSS) is a style sheet language used for describing the presentation of a document written in a markup language. It is most often used to set the visual style of web pages and user interfaces written in HTML.

\subsection{JavaScript}
 JavaScript (JS) is a high-level, dynamic, weakly typed, object-based, multi-paradigm, and interpreted programming language. Alongside HTML and CSS, JavaScript is one of the three core technologies of World Wide Web content production. It is used to make web pages interactive.

\subsection{PostgreSQL}
PostgreSQL is an object-relational database management system (ORDBMS) with an emphasis on extensibility and standards compliance. As a database server, its primary functions are to store data securely and return that data in response to requests from other software applications. It can handle workloads ranging from small single-machine applications to large Internet-facing applications (or for data warehousing) with many concurrent users. PostgreSQL is ACID-compliant and transactional. PostgreSQL has updatable views and materialized views, triggers, foreign keys; supports functions and stored procedures, and other expandability.